\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{titling}
\usepackage{color}
\usepackage{graphicx}
\usepackage[top=1.0in, bottom=1.0in, left=1.0in, right=1.0in]{geometry}
\usepackage[font=small, format=hang, up,textfont=normal,up,justification=justified,singlelinecheck=false]{caption}
\captionsetup{width=6cm}
\usepackage{wrapfig}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{vwcol}
\usepackage{enumitem}
\usepackage{afterpage}

\newcommand\blankpage{%
	\null
	\thispagestyle{empty}%
	\addtocounter{page}{-1}%
	\newpage}


\newcommand{\specialcell}[2][l]{%
  \begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}

\newcommand{\specialcellright}[2][r]{%
  \begin{tabular}[#1]{@{}r@{}}#2\end{tabular}}

\setlength\parindent{12pt}

\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\newcommand{\bigfont}{\fontsize{18}{18}\selectfont}
\newcommand{\smallfont}{\fontsize{7}{7.2}\selectfont}

\newcommand{\snn}{\sqrt{s_{_{NN}}}}



\begin{document}
%\title{Joseph D. Osborn}
%\maketitle
%\date{}

\begin{center}
\Large\textbf{Joseph (Joe) D. Osborn} \\
\normalsize Oak Ridge National Laboratory \\
osbornjd91@gmail.com \\
(859) 433-8738 \\
https://jdosbo.github.io \\
github.com/osbornjd
\end{center}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%					RESEARCH INTERESTS						%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{flushleft}
\Large\textbf{Research Interests} \\
\normalsize High-energy experimental nuclear physics, software and computing in high-energy physics.  \\ 
\end{flushleft}

%\begin{flushleft}
%\Large\textbf{Research Overview} \\
%\normalsize Experimental particle physicist with five years experience performing precision measurements of proton and nuclei structure. Possess the skill set necessary to develop complex software frameworks in Python and C++.
%\end{flushleft}








%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%					EDUCATION								%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\vspace{3pt}
\begin{flushleft}
\Large\textbf{Education} \\
\normalsize 

University of Michigan, M.S. and Ph.D. in Physics, 2018. \\
University of Kentucky, B.S. in Physics, B.S. in Mathematics, 2013.\\


\end{flushleft}

\vspace{3pt}
\begin{flushleft}
	\Large\textbf{Software and Computational Fluency} \\
	\normalsize
	Languages: C/C++, Java, Python, \LaTeX, Bash \\
	Tools: git, Jenkins, Linux, UML, Doxygen, Docker, Singularity, Serverless/FaaS\\
	HEP Packages: ROOT, ACTS, GEANT, Fun4All, RooUnfold
\end{flushleft}

\vspace{3pt}

\begin{flushleft}
\Large\textbf{Ph.D. Thesis} \\
\normalsize

		Nonperturbative factorization breaking and color entanglement effects in dihadron and direct photon-hadron angular correlations in $p$$+$$p$ and $p$$+$A collisions. J. D. Osborn, University of Michigan, May 29, 2018. hep-ex/1806.07763.
	
	\end{flushleft}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%					RESEARCH POSITIONS						%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




\vspace{3pt}
\begin{flushleft}
\Large\textbf{Research Positions} \\
%\vspace{0.2cm}
\normalsize
\vspace{-10pt}
\begin{description}[style=nextline]
	\item [\noindent Postdoctoral Research Associate, Oak Ridge National Laboratory] 07/2019-present \\
		Research Software Engineering and Application Engineering  \\
		A Common Tracking Software (ACTS) Collaboration, sPHENIX experiment at the Relativistic Heavy Ion Collider

	\item [Visiting Scholar, University of Michigan ] 06/2019-06/2020 \\
			LHCb experiment at the Large Hadron Collider, PHENIX and sPHENIX experiment at the Relativistic Heavy Ion Collider
	\item [Postdoctoral Research Fellow, University of Michigan ] 06/2018-06/2019 \\
	LHCb experiment at the Large Hadron Collider, PHENIX and sPHENIX experiments at the Relativistic Heavy Ion Collider

	\item [Graduate Research Assistant, University of Michigan ] 07/2013-06/2018 \\
	Thesis advisor: Christine Aidala\\
	PHENIX and sPHENIX experiments at the Relativistic Heavy Ion Collider
	
	\item [Undergraduate Research Assistant, University of Kentucky] 05/2012-05/2013 \\
	Thesis advisor: Renee Fatemi\\
	STAR experiment at the Relativistic Heavy Ion Collider
	
	\item [Undergraduate Research Assistant, University of Kentucky] Summer 2011 \\
	Advisor: Ron Wilhelm \\
	Sloan Digital Sky Survey search for blue giant stars
	
	\item [High School Senior Research Assistant, University of Kentucky]  01/2008-05/2009 \\
	Thesis advisor: James McDonough \\
	Hydrodynamic simulations of type IIa supernovae

\end{description}





\end{flushleft}



\vspace{7pt}

\begin{flushleft}
	\Large\textbf{Research Funding}
	\vspace{4pt}
	\normalsize
	\begin{center}
		\begin{enumerate}
			\item Oak Ridge National Laboratory subcontract through Brookhaven National Laboratory. \textit{Software Development for sPHENIX}. 03/2020-03/2021. PI, \$132k.
		\end{enumerate}
	\end{center}
\end{flushleft}


\vspace{7pt}

\begin{flushleft}
\Large\textbf{Peer Reviewed Publications with Significant Contribution}
\vspace{4pt}

\small 
Full publication list at end of CV
\begin{center}
\normalsize
\begin{enumerate}
	\item U. A. Acharya et al. (PHENIX Collaboration), ``Transverse single-spin asymmetries of midrapidity $\pi^0$ and $\eta$ mesons in polarized $p$$+$$p$ collisions at $\sqrt{s}=200$ GeV.'' arXiv:2011.14170, Submitted to Phys. Rev. D.
	
	\item J. D. Osborn for the sPHENIX Collaboration, ``Requirements, status, and plans for track reocnstruction at the sPHENIX experiment.'' arXiv:2007.00771, peer reviewed Connecting the Dots 2020 Workshop proceedings.
	
	\item U. Acharya et al. (PHENIX Collaboration), ``Measurement of jet-medium interactions via direct photon-hadron correlations in Au+Au and $d+$Au collisions at $\sqrt{s_{_{NN}}}=200$ GeV.'' Phys. Rev. C 102, 054910 (2020).
	
	\item C. A. Aidala et al. ``Design and beam test results for the 2D projective sPHENIX electromagnetic calorimeter prototype.'' arXiv:2003.13685, accepted by IEEE TNS.
	
	\item I. Helenius, J. Lajoie, J. D. Osborn, P. Paakkinen, H. Paukkunen, ``Nuclear gluons at RHIC in a multi-observable approach.'' Phys. Rev. D 100, 014004 (2019).
	
	\item A. Aaij et al. (LHCb Collaboration), ``Measurement of charged-hadron production in $Z$-tagged jets in proton-proton collisions at $\sqrt{s}=8$ TeV.'' Phys. Rev. Lett. 123, 232001 (2019).
	
	\item C. Aidala et al. (PHENIX Collaboration), ``Nonperturbative transverse momentum broadening in dihadron angular correlations in $\sqrt{s_{_{NN}}}$=~200 GeV proton-nucleus collisions.''  Phys. Rev. C 99, 044912 (2019).

	\item J. D. Osborn for the PHENIX Collaboration, ``PHENIX results on jet modification with $\pi^0$- and photon-triggered two particle correlations in $p$$+$$p$, $p(d)$+Au, and Au+Au collisions.'' Nuclear Physics A 982, 591-594 (2019).

	\item C. Aidala et al. (PHENIX Collaboration), ``Nonperturbative transverse momentum dependent effects in dihadron and direct photon-hadron angular correlations in $p$$+$$p$ collisions at $\sqrt{s}=200$ GeV.'' Phys. Rev. D 98, 072004 (2018).
		
		
	\item C. Aidala et al. (PHENIX Collaboration), ``Single-spin asymmetry of $J/\psi$ production in $p$$+$$p$, $p$+Al, and $p$$+$Au collisions with transversely polarized proton beams at $\snn$~=~200 GeV.'' Phys. Rev. D 98, 012006 (2018).
	
	\item J. D. Osborn for the PHENIX Collaboration, ``Study of cold and hot nuclear matter effects on jets with direct photon triggered correlations from PHENIX.'' Nuclear Physics A 967, 476-479 (2017).
	
	\item A. Adare et al. (PHENIX Collaboration), ``Nonperturbative-transverse-momentum effects and evolution in dihadron and direct photon-hadron angular correlations in $p$$+$$p$ collisions at $\sqrt{s}=510$ GeV.''  Phys. Rev. D95, 072002 (2017).
	
\end{enumerate}
\end{center}
\end{flushleft}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%					OTHER PUBLICATIONS						%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%				CONFERENCE PROCEEDINGS					%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\vspace{0.5cm}
\begin{flushleft}
	\Large\textbf{Conference Proceedings} \\
	\normalsize 
	\begin{enumerate}
		\item \textbf{Jet hadronization at LHCb.} Proceedings for the 13$^{th}$ International Workshop on High-$p_T$ Physics in the RHIC/LHC Era, Knoxville, TN, March 19-22, 2019. arXiv:1905.11894.
		\item \textbf{Nonperturbative transverse momentum effects in dihadron and direct photon-hadron angular correlations}, J. D. Osborn for the PHENIX Collaboration. Proceedings for the SPIN 2016 Symposium, Urbana, IL, September 25-30 2016. arXiv:1701:00681.
		\item \textbf{Parton dynamics at PHENIX}, J. D. Osborn for the PHENIX Collaboration. Proceedings for the American Physical Society Division of Particles and Fields Conference, Ann Arbor, MI, August 4-8 2015. arXiv:1511.00016. 
		
	\end{enumerate}
\end{flushleft}


\vspace{7pt}


\begin{flushleft}

\vspace{7pt}
\Large\textbf{Other Public Notes with Significant Contribution} \\
\vspace{2pt}
	\begin{center}
	\normalsize
	\begin{enumerate}
		\item sPHENIX Conceptual Design Report (CDR). The sPHENIX Collaboration. \textcolor{red}{\href{https://indico.bnl.gov/event/4640/}{https://indico.bnl.gov/event/4640}}, 2018.
		 \item Detector design study for an EIC detector around the sPHENIX solenoid. C. Aidala et al. \textcolor{red}{\href{https://indico.bnl.gov/event/5283/}{https://indico.bnl.gov/event/5283/}}, 2018.
		 \item sPHENIX medium energy barrel physics. The sPHENIX Collaboration. \textcolor{red}{\href{https://indico.bnl.gov/event/3866/}{https://indico.bnl.gov/event/3866/}}, 2017.
 		 \item T1044-2017 sPHENIX test beam EMCal analysis. J. D. Osborn and J. Huang. \textcolor{red}{\href{https://indico.bnl.gov/event/3854/}{https://indico.bnl.gov/event/3854/}}, 2017.
		\item sPHENIX modest forward upgrade LOI. The sPHENIX Collaboration. \textcolor{red}{\href{https://indico.bnl.gov/event/3867/}{https://indico.bnl.gov/event/3867}}, 2017.

	

\end{enumerate}

\end{center}

\end{flushleft}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%					SEMINARS								%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{7pt}

\begin{flushleft}
\Large\textbf{Invited Conference and Workshop Presentations}
\normalsize
\begin{enumerate}
	\item Resummation, Evolution, Factorization Workshop, December 7-11, 2020. ``Experimental perspective on hadronization.''
	\item Jets for 3D Imaging Workshop, November 23-25, 2020. ``Jet substructure at the EIC.''
	\item ACTS Workshop, May 25-29, 2020. ``sPHENIX Experience with Acts.''
	\item Second EIC Yellow Report Workshop at Pavia University, May 20-22, 2020. ``Inclusive and heavy flavor jet substructure at the EIC.''
	\item Connecting The Dots Workshop, April 22-24, 2020. ``Requirements, status and plans for track reconstruction of the sPHENIX experiment.''
	\item 3$^{rd}$ JETSCAPE Workshop, March 18-20, 2020. ``Hadronization and jet substructure at RHIC and the LHC.''
	\item 13$^{th}$ International Workshop on High $p_T$ Physics in the RHIC/LHC Era, March 19-22, 2019. ``Jet hadronization at LHCb.''
	\item Workshop on Novel Probes of the Nucleon Structure in SIDIS, e+e- and pp (FF2019), March 14-16, 2019. ``Factorization breaking, color entanglement, and hadronization of jets.''
	\item Workshop on the Definition of Jets, Brookhaven National Laboratory, June 25-27, 2018. ``Probing effects from QCD color with photon-jet and dijet correlations.''
	\item CMS SMP-J Workshop Annual Workshop, January 25, 2017. ``Color entanglement and color coherence."
\end{enumerate}
\end{flushleft}


\vspace{7pt}
\begin{flushleft}
\Large\textbf{Seminars and Colloquia} \\
\normalsize
\begin{enumerate}
	\item Workflow Workshop Seminar Series, August 14, 2020. ``Data processing workflows at scattering user facilities.''
	\item University of Tennessee HEP/Nuclear/Astro Seminar, February 3, 2020. ``Jet substructure at RHIC and the LHC.''
	\item University of Kentucky HEP/Nuclear Seminar, November 7, 2019. ``Hadronization and jet substructure at RHIC and the LHC.''
	\item University of Michigan HEP/Astro/Nuclear Seminar, April 8, 2019. ``Jet substructure at RHIC and the LHC.''
	\item Oak Ridge National Laboratory Seminar, February 18, 2019. ``Peering inside protons and nuclei.''
	\item Wayne State University PAN Seminar, September 14, 2018. ``Effects from color flow in proton-proton and proton-nucleus collisions.''
	\item Paul Laurence Dunbar High School Senior Seminar, August 31, 2018. ``Career paths with a physics degree.''
	\item University of Illinois HEP/MEP Colloquium, October 23, 2017. ``Effects from color entanglement in proton-proton and proton-nucleus collisions."
 	\item University of Michigan HEP/Astro/Nuclear Seminar, November 21, 2016. ``Recent experimental results on QCD factorization breaking at RHIC."
	\item Brookhaven National Laboratory Nuclear Seminar Series, October 25, 2016. ``Recent experimental results on QCD factorization breaking at RHIC."
	\item Seminar at Columbia University, October 24, 2016. ``Recent experimental results on QCD factorization breaking at RHIC."
	
\end{enumerate}
\end{flushleft}

\vspace{7pt}










%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%		CONFERENCE AND WORKSHOP PRESENTATIONS			%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{flushleft}
\Large\textbf{Conference and Workshop Presentations} \\
\normalsize
\begin{enumerate}
\item sPHENIX Collaboration Meeting, Boulder, Colorado (virtual), July 6, 2020. ``ACTS Tracking Progress.''
\item sPHENIX Collaboration Summer Projects Workshop, June 11, 2020. ``ACTS in sPHENIX.''
\item sPHENIX Software Mega-Workfest, Brookhaven National Laboratory, January 13-17, 2020. ``Building a Fun4All Analysis Package Tutorial.''
\item sPHENIX Collaboration Meeting, Brookhaven National Laboratory, June 5-6, 2018. ``Photons and clustering in sPHENIX.''
\item Quark Matter 2018, Lido, Italy, May 13-19, 2018. ``PHENIX results on jet modification with $\pi^0$- and photon-triggered two particle correlations in $p$$+$$p$, $p$(d)+Au, and Au(Cu)+Au collisions.''

\item PHENIX Collaboration Meeting, Brookhaven National Laboratory, December 1-3, 2017. ``High $p_T$ correlations analysis highlights and future plans.''

\item RHIC Users Meeting Proton Structure Workshop, Brookhaven National Lab, June 20-23, 2017. ``Partonic structure of nucleons and nuclei at sPHENIX."

\item Quark Matter 2017, Chicago, Illinois, February 5-11, 2017. ``Study of cold and hot nuclear matter effects on jets with direct photon-triggered correlations from PHENIX."


\item 22$^{\rm nd}$ International Spin Symposium, Urbana, IL, September 25-30, 2016. ``Nonperturbative transverse momentum effects in dihadron and direct photon-hadron angular correlations."

\item 4th Workshop on the QCD Structure of the Nucleon (QCD-N'16), Getxo, Spain, July 11-15, 2016. ``Nonperturbative transverse momentum effects in dihadron and direct photon-hadron angular correlations."

\item American Physical Society Division of Nuclear Physics Meeting, Sante Fe, NM, October 28-31, 2015. ``Measuring intrinsic partonic transverse momentum via two-particle correlations in PHENIX."

\item American Physical Society Division of Particles and Fields Meeting, Ann Arbor, MI, August 3-7, 2015. ``Parton dynamics at PHENIX." 

\item Physics Graduate Student Symposium, July 8, 2015.  ``Partonic dynamics in high energy proton-proton collisions at PHENIX." 

\item American Physical Society Southeastern Section Meeting, Tallahassee, FL, November 14-17, 2012.  ``Noise analysis of the Forward GEM Tracker at STAR." 

\item P.L. Dunbar Math Science and Technology Research Symposium, Lexington, KY, April 26, 2009. ``Neutrinos and shock reignition in the gain region of type IIa supernovae."
\end{enumerate}

\end{flushleft}

\vspace{7pt}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%			SCHOOLS/WORKSHOPS ATTENDED					%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%\begin{flushleft}
%\Large\textbf{Workshops Attended}
%\normalsize
%(No presentations given)
%\begin{enumerate}
	%\item Streaming Readout V Workshop. Brookhaven National Laboratory. November 13-15, 2019.
	%\item TMD Summer School. Temple University, June 22-28, 2017.
	%\item Emerging Spin and Transverse Momentum Effects in $p$$+$$p$ and $p$+A Collisions. RBRC Workshop. Brookhaven National Laboratory, Upton, NY, February 8-10, 2016.
%	\item PHENIX SpinFest 2014. University of Illinois, July 14-31, 2014.
%\end{enumerate}

%\end{flushleft}

\vspace{7pt}






%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%					TEACHING								%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




\begin{flushleft}
\Large \textbf{Student Advising and Mentorship}\\
\normalsize
\vspace{0.3cm}
\textbf{Graduate Students Supervised}\\
Dillon Fitzgerald - Jet Substructure and Hadronization at the EIC. \\
Kara Mattioli - Heavy flavor jet tagging and substructure at LHCb. \\
Jordan Roth - $Z^0$-hadron and $Z^0$-jet correlations analysis in LHCb $\sqrt{s}=13$ TeV $p$$+$$p$. \\
Nicole Lewis - Direct photon single spin asymmetry analysis in PHENIX $\sqrt{s}=200$ GeV $p$$+$$p$. \\

\vspace{0.5cm}

\textbf{University Research Opportunity Program (UROP) at University of Michigan}, 09/2018-05/2019\\
Propose and guide a research project to an undergraduate student. Supervised Brandon Liang in a jet substructure Monte Carlo study to better understand nonperturbative contributions to jets.\\
\vspace*{0.3cm}

\textbf{Additional Undergraduate Students Supervised}\\
Nikhil Shankar, Hayden Hansen, Ezra Lesser, Nick Melekian, Ruby Araj, Emily Camras, Robert Read, Robert Cernak, Aaron White.
\end{flushleft}




\vspace{7pt}
\begin{flushleft}
\Large\textbf{Teaching} \\
\normalsize 
\vspace{-4pt}

\begin{description}[style=nextline]
	\item [University of Michigan] \hfill
		\vspace{-0.5cm}
		\begin{enumerate}
			\item Physics for the Life Sciences Laboratory 1: Fall 2013, Spring 2014, Fall 2014, Fall 2017
			
		\end{enumerate}
	\item [University of Kentucky] \hfill
		\vspace{-0.5cm}
		\begin{enumerate}
			\item Physics 241 - General University Physics Laboratory: Fall 2012
			\item Arts and Sciences Wired Course - Measuring Science: Fall 2011
		\end{enumerate}
\end{description}


%\begin{tabular}{lll}
%\vspace{0.5cm}
%University of Michigan & Physics for the Life Sciences Laboratory 1 & \hspace{0.35cm} \specialcell{Fall 2013\\Spring 2014\\Fall 2014} \\
%University of Kentucky & Physics 241: General University Physics Laboratory & \hspace{0.45cm}Fall 2012 \\
% & Arts and Sciences Wired Course: Measuring Science & \hspace{0.45cm}Fall 2011\\
%\end{tabular}


\end{flushleft}












%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%					AWARDS AND FELLOWSHIPS				%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\vspace{7pt}
\begin{flushleft}
\Large\textbf{Awards and Fellowships} \\
\normalsize

\begin{tabular}{ll}

RHIC/AGS Users' Executive Committee Merit Award & 05/2019\\
Young PHENIXian award & 12/2015\\
Michigan Graduate $1^{st}$ Year Fellowship & 08/2013-08/2014 \\
Summa Cum Laude honors upon graduation from University of Kentucky & 05/2013 \\
Sigma Pi Sigma Physics Honor Society & 05/2013 \\
University of Kentucky Outstanding Senior Award & 05/2013\\
\end{tabular}
\end{flushleft}










%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%					CONFERENCE ORGANIZATION				%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\vspace{7pt}
\begin{flushleft}
\Large\textbf{Conference Organization} \\
\normalsize 
\begin{enumerate}
	\item LHCP Conference QCD Organizing Committee, Paris, France, June 7-12, 2021.
	\item Spin and EIC workshops at the RHIC All Users Meeting, Brookhaven National Laboratory, June 2-5, 2019.
	\item Scientific Secretary, American Physical Society Division of Particles and Fields Meeting, Ann Arbor, MI, August 3-7, 2015.
\end{enumerate}
\end{flushleft}

\vspace{7pt}







%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%					OTHER EXPERIENCE						%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




\begin{flushleft}
\Large\textbf{Collaboration and Research Community Service} \\
\normalsize 
\vspace{0.3cm}
\textbf{DOE Office of NP SBIR Proposal Reviewer} \\ Review SBIR proposals related to computing in Nuclear Physics. \\
\vspace*{0.2cm}
\textbf{Nuclear Physics Day on Capitol Hill}, 04/2018. \\ Met with staff members of Michigan Senators and Representatves to discuss funding for nuclear physics research.\\
\vspace*{0.2cm}
\textbf{Elected member, PHENIX Executive Council}, 01/2016-01/2017.\\ The Executive Council is responsible for establishing scientific priorities for the experiment. Two junior members are elected for their commitment to the experiment and representation of junior members, defined as graduate students, postdocs, and early term faculty members.



\end{flushleft}




%
%
% PAGE BREAK FOR FULL PUBLICATION LIST
%

\newpage



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%			PAPERS SUBMITTED FOR PUBLICATION				%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cleardoublepage

\begin{flushleft}

\huge\textbf{Complete Publication List}
\vspace{0.5cm}

{\large For the most up-to-date list, search `find a J. D. Osborn' on \href{inspirehep.net}{inspirehep.net} \\}
\vspace{0.5cm}
\Large\textbf{Papers Submitted for Peer Reviewed Publication or on arXiv} \\
\normalsize
\begin{center}
	\begin{flushleft}
	
	\begin{enumerate}
	
	\end{enumerate}
	
	%\vspace{1cm}
	\large PHENIX and LHCb Collaboration Papers\\ (significant contribution made to those in \textbf{\textit{bold italic text}}) \\
	\end{flushleft}
	\begin{enumerate}
			\item Transverse momentum dependent forward neutron single spin asymmetries in transversely polarized $p$$+$$p$ collisions at $\sqrt{s}=200$ GeV. U. A. Acharya et al, arXiv:2011.14187. Submitted to Phys. Rev. D.
			
			\item {\bf{\textit{Transverse single-spin asymmetries of midrapidity $\pi^0$ and $\eta$ mesons in polarized $p$$+$$p$ collisions at $\sqrt{s}=200$ GeV}}}. U. A. Acharya et al, arXiv:2011.14170. Submitted to Phys. Rev. D.
			
		\item Searches for 25 rare and forbidden decays of $D^+D_s^+ $ mesons. R. Aaij et al, arXiv:2011.00217. Submitted to JHEP.

		\item First observation of the decay $\Lambda_b^0 \to \eta_c(1S) p K^-$. R. Aaij et al, arXiv:2007.11292. Submitted to Phys. Rev. D.
	
		\item Production of $\pi^0$, $\eta$, and $K_S$ mesons in U+U collisions at $\sqrt{s_{_{NN}}}=192$ GeV. U. Acharya et. al. arXiv:2005.14686. Submitted to Phys. Rev. C.

		\item Measurement of the branching fractions for $B^+\to D^{*+}D^-K^+$, $B^+\to D^{*-}D^+K^+$, and $B^0\to D^{*-}D^0K^+$ decays. R. Aaij et al. arXiv:2005.10264. Submitted to JHEP.		
		
		\item Measurement of the shape of the $B_s^0\rightarrow D_s^{*-}\mu^+\nu_\mu$ differential decay rate. R. Aaij et al. arXiv:2003.08453. Submitted to JHEP.
				
		\item Strong constraints on the $K_s^0\rightarrow\mu^+\mu^-$ branching fraction. R. Aaij et al. arXiv:2001.10354. Submitted to Phys. Rev. Lett.
	
			
		\item Correlations of $\mu\mu$, $e\mu$, and $ee$ pairs in $p$$+$$p$ collisions at $\sqrt{s}=200$ GeV and implications for $c\bar{c}$ and $b\bar{b}$ production mechanisms. C. Aidala et al. arXiv:1805.04075. Submitted to Phys. Rev. D.
		\item An Upgrade Proposal from the PHENIX Collaboration. A. Adare et al. (PHENIX Collaboration). arXiv:1501.06197.
		\item Concept for an Electron Ion Collider (EIC) detector built around the BaBar solenoid. A. Adare et al. (PHENIX Collaboration). arXiv:1402.1209.
		
\end{enumerate}
	
\end{center}


\end{flushleft}









%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%				PUBLICATIONS IN JOURNALS					%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%





\begin{flushleft}

\vspace{7pt}
\Large\textbf{Peer Reviewed Publications}\\
\vspace{2pt}
\begin{center}
\normalsize
\begin{enumerate}
	\item \textbf{\textit{Design and beam test results for the 2D projective sPHENIX electromagnetic calorimeter prototype.}} C. A. Aidala et al.  arXiv:2003.13685. Accepted by IEEE TNS.
	
	\item\textbf{\textit{Requirements, status, and plans for track reconstruction at the sPHENIX experiment}}. J. D. Osborn for the sPHENIX Collaboration, arXiv:2007.00771. Proceedings of Connecting the Dots Workshop 2020.
	\item \textbf{\textit{Nuclear gluons at RHIC in a multi-observable approach.}} I. Helenius, J. Lajoie, J. D. Osborn, P. Paakkinen, H Paukkunen. Phys. Rev. D 100, 014004 (2019).
	\item \textbf{\textit{PHENIX results on jet modification with $\pi^0$- and photon-triggered two particle correlations in $p$$+$$p$, $p(d)$+Au, and Au+Au collisions,}} J. D. Osborn for the PHENIX Collaboration. Nuclear Physics A 982, 591-594 (2019).
	\item \textbf{\textit{Study of cold and hot nuclear matter effects on jets with direct photon triggered correlations from PHENIX,}} J. D. Osborn for the PHENIX Collaboration. Nuclear Physics A 967, 476-479 (2017).
\end{enumerate}

\vspace{14pt}
\begin{flushleft}
\large PHENIX and LHCb Collaboration Papers\\ (significant contribution made to those in \textbf{\textit{bold italic text}})\\
\end{flushleft}

\begin{enumerate}
	\normalsize
		\item Search for the doubly heavy $\mathit{\Xi}_{bc}^{0}$ baryon via decays to $D^0pK^-D$. JHEP 11, 095 (2020).
		\item Observation of enhanced double parton scattering in proton-lead collisions at $\sqrt{s_\mathrm{NN}}=$8.16 TeV. Phys. Rev. Lett. 125, 212001 (2020).
		\item Searches for low-mass dimuon resonances. JHEP 10, 156 (2020).
		\item Observation of structure in the $J/\psi$-pair mass spectrum. Science Bulletin 65, 23, 1983-1993 (2020).
		
		\item Search for $CP$ violation in $\Xi_c^+\rightarrow pK^-\pi^+$ decays using model-independent techniques. Eur. Phys. J. C 80 (2020) 10, 986.
		\item \textbf{\textit{Measurement of jet-medium interactions via direct photon-hadron correlations in Au+Au and $d+$Au collisions at $\sqrt{s_{_{NN}}}=200$ GeV.}} Phys. Rev. C 102, 054910 (2020).
		\item Polarization and cross section of midrapidity $J/\psi$ production in proton-proton collisions at $\sqrt{s}=510$ GeV. Phys.Rev.D 102, 072008 (2020)
		
		\item Production of $b\bar{b}$ at forward rapidity in $p$$+$$p$ collisions at $\sqrt{s}=$510 GeV. Phys.Rev.D 102, 092002 (2020).
		\item Study of the lineshape of the $\chi_{c1}(3872)$ state. Phys.Rev.D 102, 092005 (2020).
		\item First branching fraction measurement of the suppressed decay $\Xi_c^0\to \pi^-\Lambda_c^+$. Phys. Rev. D 102, 071101 (2020).
		\item First observation of the decay $B^0\rightarrow D^0\bar{D}^0K^+\pi^-$. Phys. Rev. D 102, 051102 (2020).
			\item Study of the $\psi_2(3823)$ and $\chi_{c1}$(3872) states in $B^+\to(J/\psi\pi^+\pi^-)K^-$ decays. JHEP 08, 123 (2020).
		\item Precision measurement of the $B_{c}^{+}$ meson mass. JHEP 07, 123 (2020).
			\item Measurement of the $\Lambda^0_b\rightarrow J/\psi\Lambda$ angular distribution and the $\Lambda^0_b$ polarisation in $pp$ collisions. JHEP 06, 110 (2020).
			\item Observation of new $\Xi_c^0$ baryons decaying to $\Lambda_c^+K^-$. Phys. Rev. Lett. 124, 222001 (2020).
			\item Measurement of $CP$ averaged observables in the $B^0\rightarrow K^{*0}\mu^=\mu^-$ decay. Phys. Rev. Lett. 125, 011802 (2020).
			\item Search for the lepton flavour violating decay $B^+\rightarrow K^+\mu^-\tau^+$ using $B_{s2}^{*0}$ decays. JHEP 06, 129 (2020).
		\item Search for the rare decays $B_s^0\rightarrow e^+e^-$ and $B^0\rightarrow e^+e^-$. Phys. Rev. Lett. 124, 211802 (2020).
		\item Measurement of charged pion double spin asymmetries at midrapidity in longitudinally polarized $p$$+$$p$ collisions at $\sqrt{s}=510$ GeV. Phys. Rev. D 102, 032001 (2020).
		\item Measurement of $CP$ observables in $B^\pm\rightarrow DK^\pm$ and $B^\pm\rightarrow D\pi^\pm$ with $D\rightarrow K_s^0K^\pm\pi^\mp$ decays. JHEP 06, 058 (2020).
		\item Observation of a new baryon state in the $\Lambda_b^0\pi^+\pi^-$ mass spectrum. JHEP 06, 136 (2020).
		\item Search for $CP$ violation and observation of $P$ violation in $\Lambda_b^0\rightarrow p\pi^-\pi^+\pi^-$ decays. Phys. Rev. D 102, 051101 (2020).
		\item Measurement of the branching fraction of the decay $B_s^0\rightarrow K_s^0K_s^0$. Phys. Rev. D 102, 012011 (2020)
		\item Measurement of $J/\psi$ at forward and backward rapidity in $p$$+$$p$, $p$$+$Al, $p$$+$Au, and $^3$He$+$Au collisions at $\snn$=200 GeV. Phys. Rev. C .102, 014902 (2020).
		\item Measurement of $|V_{cb}|$ with $B_s^0\rightarrow D_s^{(*)-}\mu^+\nu_\mu$ decays. Phys. Rev. D 101, 072004 (2020).
	\item Test of lepton universality with $\Lambda_b^0\rightarrow pK^-\ell^+\ell^-$ decays. JHEP 20, 040 (2020).
			\item Measurement of $CP$ violation in $B^0\rightarrow D^{*\pm}D^\mp$ decays. JHEP 03, 147 (2020).
		\item Observation of the semileptonic decay $B^+\rightarrow p\bar{p}\mu^+\nu_{\mu}$. JHEP 03, 146 (2020).
		\item Measurement of $f_s/f_u$ variation with proton-proton collision energy and kinematics. Phys. Rev. Lett. 124, 122002 (2020).
		\item First observation of excited $\Omega_b^-$ states. Phys. Rev. Lett. 124, 082002 (2020).
		\item $J/\psi$ and $\psi(2S)$ production at forward rapidity in $p$$+$$p$ collisions at $\sqrt{s}=510$ GeV. Phys. Rev. D 101, 052006 (2020).
		\item Isospin amplitudes in $\Lambda_{b}^0\rightarrow J/\psi\Lambda(\Sigma^0)$ and $\Xi_b^0\rightarrow J/\psi\Xi^0(\Lambda)$ decays. Phys. Rev. Lett. 124, 111802 (2020).
	 	\item Precision measurement of the $\Xi_{cc}^{++}$ mass. JHEP 2002, 049 (2020).
		\item Determination of quantum numbers for several excited charmed mesons observed in $B^-\rightarrow D^{*+}\pi^-\pi^-$  decays. Phys. Rev. D 101, 032005 (2020).
		\item Measurement of the $\eta_c(1S)$ production cross-section in $pp$ collisions at $\sqrt{s}=13$~TeV. Eur. Phys. J. C 80, 191 (2020).
	    \item Nuclear modification factor of charged hadrons at forward and backward rapidity in $p$+Al and $p$+Au collisions at $\snn=200$ GeV. Phys. Rev. C 101, 034910 (2020).
		\item Updated measurement of decay-time-dependent CP asymmetries in $D^0\rightarrow K^+K^-$ and $D^0\rightarrow\pi^+\pi^-$ decays. R. Aaij et al. Phys.Rev. D101, 012005 (2020).
		\item Measurement of $\Xi_{cc}^{++}$ production in $pp$ collisions at $\sqrt{s} = 13$~TeV. Chin. Phys. C 44, 022001 (2020).
		\item Amplitude analysis of the $B^+\rightarrow\pi^+\pi^+\pi^-$ decay. R. Aaij et al. Phys.Rev. D 101, 012006 (2020).
		\item Observation of several sources of $CP$ violation in $B^+\rightarrow\pi^+\pi^+\pi^-$ decays. R. Aaij et al. Phys.Rev.Lett. 124, 031801 (2020).
		\item Search for $A^\prime\rightarrow\mu^+\mu^-$ decays. R. Aaij et al. Phys. Rev. Lett. 124, 041801 (2020).
	
		\item Search for the doubly charmed baryon $\Xi_{cc}^+$. Sci. China Phys. Mech. Astron. 63, 221062 (2020).
		\item Measurement of the electron reconstruction efficiency at LHCb. JINST 14, P11023 (2019).
		\item Measurement of the $B_c^-$ meson production fraction asymmetry in 7 and 13 TeV $pp$ collisions. R. Aaij et al. Phys.Rev. D 100, 112006 (2019).
		\item Search for the lepton-flavour violating decays $B^+\rightarrow K^+\mu^\pm e^\mp$. R. Aaij et al. Phys.Rev.Lett. 123, 241802 (2019).
		\item Measurement of $CP$ violation in the $B_s^0\rightarrow\phi\phi$ decay and search for the $B^0\rightarrow\phi\phi$ decay. R. Aaij et al. JHEP 1909, 028 (2019).
		\item \textbf{\textit{Measurement of charged-hadron production in $Z$-tagged jets in proton-proton collisions at $\sqrt{s}=8$ TeV.}} Phys. Rev. Lett. 123, 232001 (2019).
		\item Observation of new resonances in the $\Lambda_{b}^{0}\pi^+\pi^-$ system. Phys. Rev. Lett. 123, 152001 (2019)
		\item Search for the lepton-flavour-violating decays $B_s^0\rightarrow\tau^\pm\mu^\mp$ and $B^0\rightarrow\tau^\pm\mu^\mp$. Phys. Rev. Lett. 123, 211801 (2019).
		\item A search for $\Xi_{cc}^{++}\rightarrow D^+pK^-\pi^+$ decays. JHEP 1910, 124 (2019).
		\item Observation of the $\Lambda_b^0\rightarrow\chi_{c1}(3872)pK^-$ decay. JHEP 1909, 028 (2019).
		\item Measurement of $CP$ observables in the process $B^0\rightarrow DK^{*0}$ with two- and four-body $D$ decays. JHEP 1909, 041 (2019).
		\item Updated measurement of time-dependent {\it CP}-violating observables in $B_s^0\rightarrow J/\psi K^+K^-$ decays. Eur. Phys. J. C 79, 706 (2019).
		\item Precision measurement of the $\Lambda_c ^+$, $\Xi_c^+$, and $\Xi_c^0$ baryon lifetimes. Phys. Rev. D 100, 032001 (2019).
		\item Measurement of $CP$-violating and mixing-induced observables in $B_s^0\rightarrow\phi\gamma$ decays. Phys. Rev. Lett. 123, 081802 (2019).
		\item First observation of the radiative decay $\Lambda_b^0\rightarrow\Lambda\gamma$. Phys. Rev. Lett. 123, 031801 (2019).
		\item Nuclear dependence of the transverse single-spin asymmetry in the production of charged hadrons at forward rapidity in polarized $p+p$, $p+$Al, and $p+$Au collisions at $\sqrt{s_{_{NN}}}= 200$ GeV. Phys. Rev. Lett. 123, 122001 (2019).
		\item Amplitude analysis of the $B_{(s)}^0\rightarrow K^{*0}\bar{K}^{*0}$ decay and measurement of its relative branching fraction relative to the $B_s^0\rightarrow K^{*0}\bar{K}^{*0}$. JHEP 1907, 032 (2019).
		\item Near-threshold $D\bar{D}$ spectroscopy and observation of a new charmonium state. JHEP 1907, 035 (2019).
		\item Measurement of the mass difference between neutral charm-meson eigenstates. Phys. Rev. Lett. 122, 231802 (2019).
		\item Beam-energy and centrality dependence of direct-photon emission from ultra-relativistic heavy-ion collisions. Phys. Rev. Lett. 123, 022301 (2019).
		\item Observation of an excited $B_c^+$ state. Phys. Rev. Lett. 122, 232001 (2019). 
		\item Observation of a narrow pentaquark state, $P_C(4312)^+$, and of two-peak structure of the $P_c(4450)^+$. Phys. Rev. Lett. 122, 222001 (2019).
		\item Observation of CP violation in charm decays. R. Aaij et al. Phys. Rev. Lett. 122, 211803 (2019).
		\item Search for $CP$ violation in $D_s^+\rightarrow K_s^0\pi^+$, $D^+\rightarrow K_s^0K^+$, and $D^+\rightarrow\phi\pi^+$ decays. Phys. Rev. Lett. 122, 191803 (2019).
		\item Search for lepton-universality violation in $B^+\rightarrow K^+\ell^+\ell^-$ decays. Phys. Rev. Lett. 122, 191801 (2019).
		\item Measurement of two-particle correlations with respect to second- and third-order event planes in Au+Au collisions at $\sqrt{s_{_{NN}}}=200$ GeV. Phys. Rev. C99, 054903 (2019).	
		\item Measurement of charm and bottom production from semileptonic hadron decays in $p$$+$$p$ collisions at $\sqrt{s_{_{NN}}}=200$ GeV. Phys. Rev. D 99, 092003 (2019).
		\item  \textbf{\textit{Nonperturbative transverse momentum broadening in dihadron angular correlations in $\sqrt{s_{_{NN}}}$=~200 GeV proton-nucleus collisions.}} Phys. Rev. C 99, 044912 (2019).
		\item Measurements of $\mu\mu$ pairs from open heavy flavor and Drell-Yan in $p$$+$$p$ collisions at $\sqrt{s}=200$ GeV. Phys. Rev. D 99, 072003 (2019)
		\item Multi-particle azimuthal correlations for extracting event-by-event elliptic and triangular flow in Au+Au collisions at $\snn=200$ GeV. Phys. Rev. C 99, 024903 (2019).
		\item Pseudorapidity dependence of particle production and elliptic flow in asymmetric nuclear collisions of $p$+Al, $p$+Au, $d$+Au, and $^3$He+Au at $\sqrt{s_{_{NN}}}$=~200 GeV. Phys. Rev. Lett. 121, 222301 (2018).
		\item Production of $\pi^0$ and $\eta$ mesons in Cu+Au collisions at $\snn=200$ GeV. Phys. Rev. C 98, 054903 (2018).
		\item Measurement of $\phi$-meson production at forward rapidity in $p$$+$$p$ collisions at $\sqrt{s}$=510 GeV and energy dependence of $\sigma_\phi$ from $\sqrt{s}=$200 GeV to 7 TeV. Phys. Rev. D 98, 092006 (2018).
		
		\item \textbf{\textit{Nonperturbative transverse-momentum-dependent effects in dihadron and direct photon-hadron angular correlations in $p$$+$$p$ collisions at $\sqrt{s}=200$ GeV}}. Phys. Rev. D 98, 072004 (2018).	
		\item Creating small circular, elliptical, and triangular droplets of quark-gluon plasma. Nature Phys. 15, 214-220 (2019).
		\item Low-momentum direct photon measurements in Cu+Cu collisions at $\snn=200$ GeV. A. Adare et al. Phys. Rev. C 98, 054902 (2018).
		\item Cross section and longitudinal single-spin asymmetry $A_L$ for forward $W^\pm\rightarrow\mu^\pm\nu$ production in polarized $p$$+$$p$ collisions at $\sqrt{s}=510$ GeV. Phys. Rev. D 98, 032007 (2018).
		
		\item \textbf{\textit{Single-spin asymmetry of $J/\psi$ production in $p$$+$$p$, $p$+Al, and p+Au collisions with transversely polarized proton beams at $\snn$=200 GeV}}. Phys. Rev. D 98, 012006 (2018).
		
		\item Measurement of emission angle anisotropy via long-range angular correlations with high $p_T$ hadrons in $d$+Au and $p$$+$$p$ collisions at $\sqrt{s_{_{NN}}}=$~200 GeV. A. Adare et al. Phys. Rev. C 98, 014912 (2018).
		\item Measurements of mass-dependent azimuthal anisotropy in central $p$+Au, $d$+Au, and $^3$He+Au collisions at $\sqrt{s_{_{NN}}}=$200 GeV. Phys. Rev. C 97, 064904 (2018).
		\item L\'evy-stable two-pion Bose-Einstein correlations in $\sqrt{s_{_{NN}}}=200$ GeV Au+Au collisions. Phys. Rev. C 97, 064911 (2018).
		\item Measurements of multiparticle correlations in $d$+Au collisions at 200, 62.4, 39, and 19.6 GeV and $p$+Au collisions at 200 GeV and implications for collective behavior. Phys. Rev. Lett. 120, 062302 (2018).
		\item Nuclear dependence of the transverse-single-spin asymmetry for forward neutron production in polarized $p$+A collisions at $\snn$=200 GeV. Phys. Rev. Lett. 120, 022001 (2017).
		\item Measurements of azimuthal anisotropy and charged-particle multiplicity in $d$+Au collisions at $\sqrt{s_{_{NN}}}=200$,62.4, 39, and 19.6 GeV. Phys. Rev. C96, 064905 (2017).
		\item B-meson production at forward and backward rapidity in $p$$+$$p$ and Cu+Au collisions at $\sqrt{s_{_{NN}}}=$200 GeV. Phys. Rev. C96, 064901 (2017).
		\item Measurements of $e^+e^-$ pairs from open heavy flavor in $p$$+$$p$ and $d$+A collisions at $\sqrt{s_{_{NN}}}=$200 GeV. Phys. Rev. C96, 024907 (2017).
		\item Cross section and transverse single-spin asymmetry of muons from open heavy-flavor decays in polarized $p$$+$$p$ collisions at $\sqrt{s}=200$ GeV. Phys. Rev. D95, 112001 (2017).
		\item Measurements of $B\rightarrow J/\psi$ at forward rapidity in $p$$+$$p$ collisions at $\sqrt{s}=$510 GeV. Phys. Rev. D95, 092002 (2017).
	
		\item Angular decay coefficients of J/$\psi$ mesons at forward rapidity from $p$+$p$ collisions at $\sqrt{s}$=510 GeV. Phys. Rev. D95, 092003 (2017).
	
		\item \textbf{\textit{Nonperturbative-transverse-momentum effects and evolution in dihadron and direct photon-hadron angular correlations in $p$$+$$p$ collisions at $\sqrt{s}=510$ GeV.}} Phys. Rev. D95, 072002 (2017).
		
	\item Measurement of long-range angular correlations and azimuthal anisotropies in high-multiplicity $p$$+$Au collisions at $\sqrt{s_{_{NN}}}=200$ GeV. Phys. Rev. C95, 034910 (2017).
	
	\item Measurement of the relative yields of $\psi(2S)$ to $\psi(1S)$ mesons produced at forward and backward rapidity in $p$$+$$p$, $p$+Al, $p$+Au, and $^3$He+Au collisions at $\sqrt{s_{_{NN}}}=200$ GeV. Phys. Rev. C95, 034904 (2017).
	
	\item Measurements of double-helicity asymmetries in inclusive $J/\psi$ production in longitudinally polarized $p$$+$$p$ collisions at $\sqrt{s}$=510 GeV. Phys. Rev. D94, 112008 (2016).
	\item	 Azimuthally anisotropic emission of low-momentum direct photons in Au$+$Au collisions at $\sqrt{s_{_{NN}}}=200$ GeV. Phys. Rev. C94, 064901 (2016).
	\item	Measurements of directed, elliptic, and triangular flow in Cu$+$Au collisions at $\sqrt{s_{_{NN}}}=200$ GeV. Phys. Rev. C94, 054910 (2016).
	\item Inclusive cross section and double-helicity asymmetry for $\pi^0$ production at midrapidity in $p$+$p$ collisions at $\sqrt{s}$=510 GeV. Phys. Rev. D93, 011501 (2016).	
	\item	 Scaling properties of fractional momentum loss of high-$p_T$ hadrons in nucleus-nucleus collisions at $\sqrt{s_{_{NN}}}$ from 62.4 GeV to 2.76 TeV. Phys. Rev. C93, 024911 (2016).	
	\item	 Transverse energy production and charged-particle multiplicity at midrapidity in various systems from $\sqrt{s_{_{NN}}}=7.7$ to 200 GeV. Phys. Rev. C93, 024901 (2016).
	\item  $\phi$ meson production in the forward/backward rapidity region in Cu$+$Au collisions at $\sqrt{s_{_{NN}}}=200$ GeV. Phys. Rev. C93, 024904 (2016).
	\item	 Forward $J/\psi$ production in U$+$U collisions at $\sqrt{s_{_{NN}}}$=193 GeV. Phys. Rev. C93, 034903 (2016).
	\item Dielectron production in Au+Au collisions at $\sqrt{s_{_{NN}}}$=200 GeV. Phys. Rev. C93,014904 (2016).  
	\item Single electron yields from semileptonic charm and bottom hadron decays in Au+Au collisions at $\sqrt{s_{_{NN}}}$=200 GeV. Phys. Rev. C93, 034904 (2016).
	\item Centrality-dependent modification of jet-production rates in $d+$Au collisions at $\sqrt{s_{_{NN}}}$=200 GeV. Phys. Rev. Lett. 116, 122301 (2016).
	\item Measurements of elliptic and triangular flow in high-multiplicity $^{3}$He$+$Au collisions at $\sqrt{s_{_{NN}}}=200$GeV. Phys. Rev. Lett 115, 142301(2015).
	\item $\phi$ meson production in $d$$+$Au collisions at $\sqrt{s_{_{NN}}}=200$ GeV. Phys. Rev. C92, 044909(2015).	
	\item Measurement of parity-violating spin asymmetries in W$^\pm$ production at midrapidity in longitudinally polarized $p$$+$$p$ collisions. Phys. Rev. D 93,051103 (2015).
	\item Systematic study of charged-pion and kaon femtoscopy in Au+Au collisions at $\sqrt{s_{_{NN}}}=200$ GeV. Phys. Rev. C92, 034914 (2015).
\end{enumerate}

\end{center}



\end{flushleft}










\vspace{7pt}


































%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%					REFERENCES								%%%%%%%%%%
%%%%%%%															%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%
%\begin{flushleft}
%\Large\textbf{References}\\
%\normalsize
%\vspace{0.3cm}
%
%\begin{tabular}{lll}
%\specialcell{Christine Aidala \\
%Associate Professor \\
%University of Michigan \\
%caidala@umich.edu \\
%(734) 764-1795 }
%&
%\hspace*{1.5cm}
%
%\specialcell{Jin Huang \\
%Associate Physicist \\
%Brookhaven National Laboratory \\
%jhuang@bnl.gov \\
%(631) 344-5898 
%}
%&
%\hspace*{1.5cm}
%\specialcell{Renee Fatemi \\
%Associate Professor \\
%University of Kentucky \\
%rfatemi@pa.uky.edu \\
%(859) 257-2664 \\
%}
%\end{tabular}
%
%\end{flushleft}
%








\end{document}
